---
title: "Pilot analysis"
output: html_notebook
---


```{r}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


```{r}
library(dplyr)
library(tidyr)
library(langcog)
library(ggplot2)
library(ggthemes)
library(forcats)
library(knitr)
theme_set(theme_few())

data.path <- "~/Documents/research/causals/data/pilots/"

readData <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-trials.csv", sep = "")))
}

readCatchTrials <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-catch_trials.csv", sep = "")))
}


readSubjectInfo <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-subject_information.csv", sep = "")))
}
```

# Pilot 1

```{r}
d.info <- readSubjectInfo("pilot-causals-1")

print(mean(d.info$enjoyment))

table(d.info$enjoyment)
```


```{r}
d <- readData("pilot-causals-1")
```

## Time

Total time spent on experiment

```{r fig.width=5}
d %>% 
  group_by(workerid) %>% 
  summarize(totalMin = sum(rt/1000/60)) %>%
  ggplot(., aes(x = totalMin))+
  geom_histogram()
```

Time on each trial (first trial in red)

```{r fig.width=5}
d %>%
  ggplot(., aes(x = rt / 1000, fill = trial_num == 0))+
  geom_histogram(position = position_dodge())+
  scale_fill_solarized()+
  xlab("seconds")+
  xlim(0, 200)
```

## Prior questions

```{r}
d %>%
  group_by(query, distribution) %>%
  summarize(n = n()) %>%
  kable()
```



```{r fig.width=5.0, fig.height = 6}
d %>% 
  select(story, target, distribution, starts_with("prior")) %>%
  gather(key, val, starts_with("prior")) %>%
  separate(key, into = c("key", "question")) %>%
  mutate(question = fct_relevel(question, "probabilityOfPresent"),
         distribution = fct_relevel(distribution, 
                                    "rare", "accidental", 
                                    "gendered", "female", 
                                    "prevalent", "biological")) %>%
  ggplot(., aes( x = val, fill = distribution))+
  geom_histogram()+
  facet_grid(distribution~question)+
  theme(strip.text.y = element_text(angle = 0))+
  scale_fill_solarized()+
  guides(fill = F)
```

Domain differences in extendability?
```{r}
d %>% 
  select(story, target, distribution, starts_with("prior")) %>%
  gather(key, val, starts_with("prior")) %>%
  separate(key, into = c("key", "question")) %>%
  mutate(question = fct_relevel(question, "probabilityOfPresent"),
         distribution = fct_relevel(distribution, 
                                    "rare", "accidental", 
                                    "gendered", "female", 
                                    "prevalent", "biological")) %>%
  filter(question == "prevalenceGivenPresent") %>%
  ggplot(., aes( x = val, fill = distribution))+
  geom_histogram()+
  facet_grid(distribution~story)+
  theme(strip.text.y = element_text(angle = 0))+
  scale_fill_solarized()+
  guides(fill = F)
```


## Listener data

```{r fig.width=8, fig.height = 3}
d %>% 
  filter(condition == "listener") %>%
  select(story, target, distribution, posterior) %>%
  mutate(distribution = fct_relevel(distribution, "rare", "accidental", "gendered", "female", "prevalent", "biological")) %>%
  ggplot(., aes( x = posterior, fill = distribution))+
  geom_histogram()+
  facet_grid(.~distribution)+
  #theme(strip.text.y = element_text(angle = 0))+
  scale_fill_solarized()+
  guides(fill = F)+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))
```



### Compare listener and prior prevalenceWhenPresent

```{r}
d.listener.prior <- d %>% 
  filter(condition == "listener") %>%
  select(story, target, distribution, prior_prevalenceGivenPresent, posterior) %>%
  gather(key, val, prior_prevalenceGivenPresent, posterior) %>%
  mutate(distribution = fct_relevel(distribution, "rare", "accidental", "gendered", "female", "prevalent", "biological")) %>%
  group_by(distribution, key) %>%
  multi_boot_standard(column = "val")

d.listener.prior %>%
  select(-ci_lower, -ci_upper) %>%
  spread(key, mean) %>%
  ungroup() %>%
  summarize(correlation = cor(prior_prevalenceGivenPresent, posterior))

left_join(
  d.listener.prior %>%
    filter(key == "posterior") %>%
    rename(listener = mean, 
           listener_upper = ci_upper, listener_lower = ci_lower) %>%
    select(-key),
  d.listener.prior %>%
    filter(key == "prior_prevalenceGivenPresent") %>%
    rename(prior = mean, 
           prior_upper = ci_upper, prior_lower = ci_lower) %>%
    select(-key)
  ) %>%
  ggplot(., aes( x = prior, xmin = prior_lower, xmax =prior_upper,
                 y = listener, ymin = listener_lower, ymax = listener_upper,
                 color = distribution))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange()+
  geom_errorbarh(width = 0.1)+
  geom_point()+
  xlim(0, 1)+
  ylim(0, 1)+
  coord_fixed()+
  scale_color_solarized()
```

## Speaker data


```{r}
d %>% 
  filter(condition == "speaker", frequency %in% c(10)) %>%
  mutate(distribution = fct_relevel(distribution, "rare", "accidental", "gendered", "female", "prevalent", "biological")) %>%
  group_by(distribution, frequency) %>%
  summarize(n = n()) %>%
  kable()
```


```{r}
d %>% 
  filter(condition == "speaker", frequency %in% c(30)) %>%
  mutate(distribution = fct_relevel(distribution, "rare", "accidental", "gendered", "female", "prevalent", "biological")) %>%
  group_by(distribution, frequency) %>%
  summarize(n = n()) %>%
  kable()
```
```{r}
d %>% 
  filter(condition == "speaker", frequency %in% c(50)) %>%
  mutate(distribution = fct_relevel(distribution, "rare", "accidental", "gendered", "female", "prevalent", "biological")) %>%
  group_by(distribution, frequency) %>%
  summarize(n = n()) %>%
  kable()
```

```{r fig.width = 8, fig.height = 3.5}
d %>% 
  filter(condition == "speaker") %>%
  mutate(distribution = fct_relevel(distribution, "rare", "accidental", "gendered", "female", "prevalent", "biological")) %>%
  group_by(distribution, frequency) %>% #also, by story / target
  multi_boot_standard(column = "posterior") %>%
  ggplot(., aes( x = frequency, y = mean, ymin = ci_lower, ymax = ci_upper, group = distribution, fill = distribution))+
  geom_bar(stat='identity', position = position_dodge(), color = 'black')+
  geom_errorbar()+
  scale_fill_solarized()+
  scale_x_continuous(breaks = c(10, 30, 50, 70))+
  facet_grid(.~distribution)+
  guides(fill = F)+
  ylab("proportion agree with causal")
```
# Pilot 2

```{r}
d.info <- readSubjectInfo("pilot-causals-2")

print(mean(d.info$enjoyment))

table(d.info$enjoyment)
```


```{r}
d2 <- readData("pilot-causals-2")
```

## Time

Total time spent on experiment

```{r fig.width=5}
d2 %>% 
  group_by(workerid) %>% 
  summarize(totalMin = sum(rt/1000/60)) %>%
  ggplot(., aes(x = totalMin))+
  geom_histogram()
```

Time on each trial (first trial in red)

```{r fig.width=5}
d2 %>%
  ggplot(., aes(x = rt / 1000, fill = trial_num == 0))+
  geom_histogram(position = position_dodge())+
  scale_fill_solarized()+
  xlab("seconds")+
  xlim(0, 150)
```



Time in each condition

```{r fig.width=5}
d2 %>%
  ggplot(., aes(x = rt / 1000, fill = condition))+
  geom_histogram(position = position_dodge())+
  scale_fill_solarized()+
  xlab("seconds")+
  xlim(0, 150)
```


## Prior and listener data

How many in each condition

```{r}
table(d2$condition, d2$distribution) %>% kable()
```
Prior condition assignments

```{r}
with(d2 %>% filter(condition == "prior"),
  table(target, distribution)) %>% kable()
```


```{r fig.width=8, fig.height = 3}
d %>%
  filter(condition %in% c("prior", "listener")) %>%
  ggplot(., aes(x = response, fill = condition))+
  #geom_density()+
  geom_histogram(position = position_dodge(), bins = 10)+
  facet_grid(.~distribution)+
  scale_fill_grey()+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  xlab("causal power / frequency")
```

```{r}
df.listener.summary <- d %>%
  filter(condition %in% c("prior", "listener")) %>%
  mutate(distribution = fct_relevel(distribution, "rare", "accidental", "gendered", "female", "prevalent", "biological")) %>%
  group_by(condition, distribution) %>%
  multi_boot_standard(column = "response")
  
ggplot(df.listener.summary, aes(x = distribution, y = mean, ymin = ci_lower, ymax = ci_upper, fill = condition)) + 
  geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
  geom_errorbar(position = position_dodge())+
  scale_fill_grey()+
  coord_flip()+
  ylab("mean causal power / frequency")
```

## Speaker data

```{r}
with(d %>% filter(condition == 'speaker'), table(distribution, target,frequency)) %>% kable()
```


```{r fig.width=8, fig.height = 4}
d %>%
  filter(condition == "speaker") %>%
  mutate(frequency = factor(frequency),
         distribution = fct_relevel(distribution, "rare", "accidental", "gendered", "female", "prevalent", "biological")) %>%
  ggplot(., aes(x = response, fill = frequency))+
  #geom_density()+
  geom_histogram(position = position_dodge(), bins = 10)+
  facet_grid(distribution~target)+
  scale_fill_solarized()+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  theme(strip.text.y = element_text(angle = 0))+
  xlab("agreement with causal")
```

```{r}
df.speaker.summary <- d %>%
  filter(condition == "speaker") %>%
  mutate(distribution = fct_relevel(distribution, "rare", "accidental", "gendered", "female", "prevalent", "biological")) %>%
  group_by(condition, distribution, frequency) %>%
  multi_boot_standard(column = "response")
  
ggplot(df.speaker.summary, aes(x = frequency, y = mean, ymin = ci_lower, ymax = ci_upper, fill = distribution)) + 
  geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
  geom_errorbar(position = position_dodge())+
  scale_fill_solarized()+
  ylab("mean agreement with causal")
```


```{r}
df.speaker.summary.items <- d %>%
  filter(condition == "speaker") %>%
  mutate(distribution = fct_relevel(distribution, "rare", "accidental", "gendered", "female", "prevalent", "biological")) %>%
  group_by(condition, distribution, target, frequency) %>%
  multi_boot_standard(column = "response")
  
ggplot(df.speaker.summary.items, 
       aes(x = frequency, y = mean, ymin = ci_lower, ymax = ci_upper, fill = target)) + 
  geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
  geom_errorbar(position = position_dodge())+
  facet_wrap(~distribution) +
  scale_fill_solarized()+
  ylab("mean agreement with causal")
```


# Pilot 3

- One item (chemical compounds making animals *alert*).
- 3 priors (rare, accidental, prevalent)
- One target frequency: 20%

n = 90 (~ 30 / prior)

```{r}
d3.info <- readSubjectInfo("pilot-causals-3")

table(d3.info$enjoyment)
```


```{r}
d3 <- readData("pilot-causals-3")
```

Time on trial

```{r}
d3 %>%
  ggplot(., aes( x = rt / 1000))+
  geom_histogram()+
  xlab("time in seconds")
```


How many participants per distribution

```{r}
d3 %>%
  group_by(distribution) %>%
  summarize(n = n()) %>% kable()
```


```{r}
d3.summary <- d3 %>%
  group_by(target, frequency, distribution) %>%
  multi_boot_standard(column = 'response') %>%
  mutate(distribution = fct_relevel(distribution, "prevalent", "accidental", "rare"))
  

ggplot(d3.summary, aes( x = distribution, y = mean, ymin = ci_lower, ymax = ci_upper))+  
  geom_bar(stat = 'identity', position = position_dodge(0.6), width = 0.6)+
  geom_errorbar(position = position_dodge(0.6), width = 0.3) + 
  ylim(0, 1)+
  ggtitle("makes feps alert (given 20% frequency)")+
    geom_hline(yintercept = 0.5, lty = 3)
```

# Pilot 4

- One item (chemical compounds making animals *alert*).
- 3 priors (rare, accidental, prevalent)
- One target frequency: 20%

n = 90 (~ 30 / prior)

```{r}
d4.info <- readSubjectInfo("pilot-causals-4")

table(d4.info$enjoyment)
```


```{r}
d4 <- readData("pilot-causals-4")
```

Time on trial

```{r}
d4 %>%
  ggplot(., aes( x = rt / 1000))+
  geom_histogram()+
  xlab("time in seconds")
```


How many participants per distribution

```{r}
d4 %>%
  group_by(distribution) %>%
  summarize(n = n()) %>% kable()
```


```{r}
d4.summary <- d4 %>%
  group_by(target, frequency, distribution) %>%
  multi_boot_standard(column = 'response') %>%
  mutate(distribution = fct_relevel(distribution, "prevalent", "accidental", "rare"))
  

ggplot(d4.summary, aes( x = distribution, y = mean, ymin = ci_lower, ymax = ci_upper))+  
  geom_bar(stat = 'identity', position = position_dodge(0.6), width = 0.6)+
  geom_errorbar(position = position_dodge(0.6), width = 0.3) + 
  ylim(0, 1)+
  ggtitle("makes feps alert (given 20% frequency)")+
    geom_hline(yintercept = 0.5, lty = 3)
```



# Pilot 5

- Three items (*alert*, *hair turn brown*, *salivate*)
- 3 priors (rare, accidental, prevalent)
- One target frequency: 20%
- 2 conditions (prior predictive and speaker)


```{r}
d5.info <- readSubjectInfo("pilot-causals-5")

table(d5.info$enjoyment)
```

```{r}
d5.info %>% select(comments) %>% kable()
```

```{r}
d5.info %>% select(problems) %>% kable()
```


```{r}
d5 <- readData("pilot-causals-5")
```

How many participants per distribution

```{r}
d5 %>%
  group_by(distribution, story, condition) %>%
  summarize(n = n()) %>% 
  mutate(n = ifelse(condition == "prior", n / 4, n)) %>%
  kable()
```


### Prior data

```{r}
d5.prior <- d5 %>% filter(condition == "prior")

ggplot(d5.prior, aes(x = response))+
  geom_histogram()+
  facet_grid(story~distribution, scales = 'free')
```

```{r}
d5.prior %>%
  filter(distribution != "prevalent") %>%
  group_by(story, distribution) %>%
  multi_boot_standard(column = "response", na.rm = T) %>% 
  ggplot(., aes( x = distribution, fill = story, y = mean,
                 ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())
```

Probably not enough data to see differences if they were there; but also the items are probably not right.


```{r}
df5.summary <- d5 %>%
  filter(condition == "speaker") %>%
  group_by(target, frequency, story, distribution) %>%
  multi_boot_standard(column = 'response') %>%
  mutate(distribution = 
           fct_relevel(distribution, "prevalent", "accidental", "rare"))
  

ggplot(df5.summary, 
       aes( x = target, y = mean, ymin = ci_lower, ymax = ci_upper, fill = target))+  
  geom_bar(stat = 'identity', position = position_dodge(0.6), width = 0.6)+
  geom_errorbar(position = position_dodge(0.6), width = 0.3) + 
  ylim(0, 1)+
  ggtitle("makes it go (given 20% frequency)")+
  geom_hline(yintercept = 0.5, lty = 3) + 
  facet_wrap(~distribution)+
  theme(axis.text.x = element_blank())
```

Unfortunately not enough data to really see differences. 
But also, I'm starting to think that the items are not extreme enough.

# Pilot 6: Prior x Domain manipulation

- Two items (*blicket detector*, *metal rusting*)
- 1 priors (rare)
- 1 "Evidence level": P sees only results of 3 "experiments"

- 6 sliders


```{r}
d6.info <- readSubjectInfo("pilot-causals-6")

table(d6.info$enjoyment)
```

```{r}
d6.info %>% select(comments) %>%
  filter(comments != "") %>% kable()
```

```{r}
d6.info %>% select(problems) %>%  filter(problems != "") %>%kable()
```


```{r}
d6 <- readData("pilot-causals-6")
```

Time spent on trial

```{r}
d6.rt <- unique(d6 %>% select(workerid, rt)) %>%
  mutate(logrt = log(rt / 1000))


d6.rt.stats <- d6.rt %>% 
  summarize(meanRT = mean(rt / 1000),
            sdRT = sd(rt / 1000),
            meanLogRT = mean(logrt),
            sdLogRT = sd(logrt))

ggplot(d6.rt, aes( x = rt/1000))+
  geom_histogram()


d6.filtered <- d6 %>%
  filter(rt > 20*1000)
```


How many participants per distribution

```{r}
d6.filtered %>%
  group_by(distribution, story, condition) %>%
  summarize(n = n()) %>% 
  mutate(n = ifelse(condition == "prior", n / 6, n)) %>%
  kable()
```


### Prior data

```{r}
ggplot(d6.filtered, aes(x = response))+
  geom_histogram()+
  facet_grid(story~distribution, scales = 'free')+
  xlim(0, 1)
```

# Pilot 7

## Endorsement Pilot -- 6 Priors x 2 Frequency 

- Three items (though not enough power to see item differences)
- 6 priors: 
- 2 target frequencies


```{r}
d7.info <- readSubjectInfo("pilot-causals-7-endorsement")

table(d7.info$enjoyment)
```

```{r}
d7.info %>% select(comments) %>%
  filter(comments != "") %>% kable()
```

```{r}
d6.info %>% select(problems) %>%  filter(problems != "") %>%kable()
```


```{r}
d7 <- readData("pilot-causals-7-endorsement")
```

Time spent on trial

```{r}
d7.rt <- unique(d7 %>% select(workerid, rt)) %>%
  mutate(logrt = log(rt / 1000))


d7.rt.stats <- d7.rt %>% 
  summarize(meanRT = mean(rt / 1000),
            sdRT = sd(rt / 1000),
            meanLogRT = mean(logrt),
            sdLogRT = sd(logrt))

ggplot(d7.rt, aes( x = rt/1000))+
  geom_histogram()

```


How many participants per distribution

```{r}
d7 %>%
  group_by(frequency, distribution) %>%
  summarize(n = n()) %>% 
  kable()
```


### Endorsement data

```{r}
d7.summary <- d7 %>%
  group_by(distribution, frequency) %>%
  multi_boot_standard(column = 'response') %>%
  ungroup() %>%
  mutate(frequency = factor(frequency, levels = c(20, 60)),
         distribution = factor(distribution, levels = c("rare_weak", "common_weak", "rare_strong", "common_strong",
                                                        "rare_deterministic", "weak_or_strong")))
  

ggplot(d7.summary, aes( x = distribution, y = mean, ymin = ci_lower, ymax = ci_upper, fill = frequency, group = frequency))+  
  geom_bar(stat = 'identity', position = position_dodge(0.6), width = 0.6)+
  scale_fill_solarized()+
  geom_errorbar(position = position_dodge(0.6), width = 0.3) + 
  ylim(0, 1)+
  ggtitle("causal endorsement")+
  geom_hline(yintercept = 0.5, lty = 3)+
  theme(axis.text.x = element_text(angle = 90))
```

### Explore domain or prior effects, independently


#### Domain x frequency effects (collapsing across distribution)

How many participants per domain x distribution x frequency

```{r}
d7 %>%
  group_by(frequency, story) %>%
  summarize(n = n()) %>% 
  kable()
```

```{r}
d7.summary.item.collapseDist <- d7 %>%
  group_by(story, frequency) %>%
  multi_boot_standard(column = 'response') %>%
  ungroup() %>%
  mutate(frequency = factor(frequency, levels = c(20, 60)))
  

ggplot(d7.summary.item.collapseDist, aes( x = story, y = mean, ymin = ci_lower, ymax = ci_upper, fill = frequency, group = frequency))+  
  geom_bar(stat = 'identity', position = position_dodge(0.6), width = 0.6)+
  scale_fill_solarized()+
  geom_errorbar(position = position_dodge(0.6), width = 0.3) + 
  ylim(0, 1)+
  ggtitle("causal endorsement")+
  geom_hline(yintercept = 0.5, lty = 3)+
  theme(axis.text.x = element_text(angle = 90))
```


#### Distribution effects (collapsing across frequencies / domains)


How many participants per domain x distribution x frequency

```{r}
d7 %>%
  group_by(distribution) %>%
  summarize(n = n()) %>% 
  kable()
```


```{r}
d7.summary.dist.collapseFreqItem <- d7 %>%
  group_by(distribution) %>%
  multi_boot_standard(column = 'response') %>%
  ungroup() %>%
  mutate(distribution = factor(distribution, 
                               levels = c("rare_weak", "common_weak", "rare_strong", "common_strong",
                                                        "rare_deterministic", "weak_or_strong")))  


ggplot(d7.summary.dist.collapseFreqItem, 
       aes( x = distribution, y = mean, ymin = ci_lower, ymax = ci_upper))+  
  geom_bar(stat = 'identity', position = position_dodge(0.6), width = 0.6)+
  scale_fill_solarized()+
  geom_errorbar(position = position_dodge(0.6), width = 0.3) + 
  ylim(0, 1)+
  ggtitle("causal endorsement")+
  geom_hline(yintercept = 0.5, lty = 3)+
  theme(axis.text.x = element_text(angle = 90))
```


#### Domain x distribution effects


How many participants per domain x distribution

```{r}
d7 %>%
  group_by(distribution, story) %>%
  summarize(n = n()) %>% 
  kable()
```


Though the data is few, I will examine by-item

```{r fig.height = 3}
d7.summary.item <- d7 %>%
  group_by(distribution, story) %>%
  multi_boot_standard(column = 'response') %>%
  ungroup() %>%
  mutate(distribution = factor(distribution, 
                               levels = c("rare_weak", 
                                          "common_weak",
                                          "rare_strong",
                                          "common_strong",
                                          "rare_deterministic",
                                          "weak_or_strong")))
  

ggplot(d7.summary.item, aes( x = distribution, y = mean, ymin = ci_lower, ymax = ci_upper, fill = story, group = story))+  
  geom_bar(stat = 'identity', position = position_dodge(0.6), width = 0.6)+
  scale_fill_solarized()+
  geom_errorbar(position = position_dodge(0.6), width = 0.3) + 
  ylim(0, 1)+
  ggtitle("causal endorsement")+
  geom_hline(yintercept = 0.5, lty = 3)+
  theme(axis.text.x = element_text(angle = 90))
```


## Distribution by frequency (filtering out "rocks")


How many participants per distribution

```{r}
d7 %>%
  filter(story != "rocks dissolve") %>%
  group_by(frequency, distribution) %>%
  summarize(n = n()) %>% 
  kable()
```

```{r}
d7.summary.norocks <- d7 %>%
  filter(story != "rocks dissolve") %>%
  group_by(distribution, frequency) %>%
  multi_boot_standard(column = 'response') %>%
  ungroup() %>%
  mutate(frequency = factor(frequency, levels = c(20, 60)),
         distribution = factor(distribution, levels = c("rare_weak", "common_weak", "rare_strong", "common_strong",
                                                        "rare_deterministic", "weak_or_strong")))
  

ggplot(d7.summary.norocks, aes( x = distribution, y = mean, ymin = ci_lower, ymax = ci_upper, fill = frequency, group = frequency))+  
  geom_bar(stat = 'identity', position = position_dodge(0.6), width = 0.6)+
  scale_fill_solarized()+
  geom_errorbar(position = position_dodge(0.6), width = 0.3) + 
  ylim(0, 1)+
  ggtitle("causal endorsement")+
  geom_hline(yintercept = 0.5, lty = 3)+
  theme(axis.text.x = element_text(angle = 90))
```
## Prior

```{r}
d7.info <- readSubjectInfo("pilot-causals-7-prior")

table(d7.info$enjoyment)
```

```{r}
d7.info %>% select(comments) %>%
  filter(comments != "") %>% kable()
```

```{r}
d7.info %>% select(problems) %>%  filter(problems != "") %>%kable()
```


```{r}
d7 <- readData("pilot-causals-7-prior")
```

Time spent on trial

```{r}
d7.rt <- unique(d7 %>% select(workerid, rt)) %>%
  mutate(logrt = log(rt / 1000))


d7.rt.stats <- d7.rt %>% 
  summarize(meanRT = mean(rt / 1000),
            sdRT = sd(rt / 1000),
            meanLogRT = mean(logrt),
            sdLogRT = sd(logrt))

ggplot(d7.rt, aes( x = rt/1000))+
  geom_histogram()


d7.filtered <- d7 %>%
  filter(rt > 20*1000)
```


How many participants per distribution

```{r}
d7 %>%
  group_by(distribution, condition) %>%
  summarize(n = n()) %>% 
  mutate(n = ifelse(condition == "prior", n / 5, n)) %>%
  kable()
```


### Prior data

```{r fig.width = 4, fig.height = 5}
ggplot(d7, aes(x = response))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  facet_grid(distribution~., scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))+ ylab("proportion")
  
```

```{r}
ggplot(d7, aes(x = response))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  facet_grid(story~., scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))+ ylab("proportion")
```

```{r}
ggplot(d7, aes(x = response))+
  geom_histogram()+
  facet_grid(story~distribution, scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))
```

```{r}
d7 %>% filter(distribution == "rare_deterministic") %>% View()
```

## Interpretation

```{r}
d7.int.info <- readSubjectInfo("pilot-causals-7-interpretation")

table(d7.int.info$enjoyment)
```

```{r}
d7.int.info %>% select(comments) %>%
  filter(comments != "") %>% kable()
```

```{r}
d7.int.info %>% select(problems) %>%  filter(problems != "") %>%kable()
```


```{r}
d7.int <- readData("pilot-causals-7-interpretation")
```

Time spent on trial

```{r}
d7.int.rt <- unique(d7.int %>% select(workerid, rt)) %>%
  mutate(logrt = log(rt / 1000))


d7.int.rt.stats <- d7.int.rt %>% 
  summarize(meanRT = mean(rt / 1000),
            sdRT = sd(rt / 1000),
            meanLogRT = mean(logrt),
            sdLogRT = sd(logrt))

ggplot(d7.int.rt, aes( x = rt/1000))+
  geom_histogram()


d7.filtered <- d7 %>%
  filter(rt > 20*1000)
```


How many participants per distribution

```{r}
d7.int %>%
  group_by(distribution, condition) %>%
  summarize(n = n()) %>% 
  mutate(n = ifelse(condition == "prior", n / 5, n)) %>%
  kable()
```


### Interpretation data

```{r}
ggplot(d7.int, aes(x = response))+
  #geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  geom_histogram(bins=100)+
  theme(strip.text.y = element_text(angle = 0))
```


```{r fig.width = 4, fig.height = 5}
ggplot(d7.int, aes(x = response))+
  #geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  geom_histogram()+
  facet_grid(distribution~., scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))+
  ylab("proportion")
  
```

# Pilot 8

Endorsement Pilot -- 4 Prior

- Prior: 4 distributions (rare vs. common X weak vs. deterministic)
- Add catch trial at end
- Make distributions more random looking (no round numbers)
- n = 50 / distribution
- 20% target frequency

```{r}
d8.info <- readSubjectInfo("pilot-causals-8")

table(d8.info$enjoyment)
```


```{r}
d8.info %>% select(comments) %>%
  filter(comments != "") %>% kable()
```

```{r}
d8.info %>% select(problems) %>%  filter(problems != "") %>%kable()
```

```{r}
d8.catch <- readCatchTrials("pilot-causals-8")

d8.catch <- d8.catch %>% mutate(passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))
  
sum(d8.catch$passBoth)
```

```{r}
d8 <- left_join(readData("pilot-causals-8"), d8.catch %>% select(workerid, passBoth))
```


```{r}

d8.filtered <- d8 %>% filter(passBoth == 1)

d8.filtered %>%
  group_by(distribution) %>%
  summarize(n = n()) %>% kable()
```

```{r fig.width = 6}
d8.summary <- d8.filtered %>%
  group_by(distribution, frequency) %>%
  multi_boot_standard(column = "response") %>%
  ungroup()

d8.bayes <- d8.filtered %>%
  group_by(distribution, frequency) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

ggplot(d8.bayes, aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = distribution,
#ggplot(d8.summary, aes( x = factor(frequency), y = mean, ymin = ci_lower, ymax = ci_upper, fill = distribution,
                        group = distribution))+
  geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'white')+
  geom_errorbar(width = 0.2, position = position_dodge(0.3), color = 'white')+
  theme(axis.text.x = element_text(angle = 90))+
  geom_hline(yintercept = 0.5, lty = 3, color = 'white')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
  scale_fill_solarized()+
  xlab("Frequency")+
  ylab("Proportion Causal Endorsement")+
  theme_black()

ggsave("~/Documents/research/talks/generics/a-generic-workshop-2017-comgen/img/causals-pilot-8.pdf", width = 5, height = 3)
```



# Pilot 8 b

Endorsement Pilot -- 4 Prior

Same as Pilot 8, but 

- 70% target frequency

```{r}
d8b.info <- readSubjectInfo("pilot-causals-8-b")

table(d8b.info$enjoyment)
```


```{r}
d8b.info %>% select(comments) %>%
  filter(comments != "") %>% kable()
```

```{r}
d8b.info %>% select(problems) %>%  filter(problems != "") %>%kable()
```

```{r}
d8b.catch <- readCatchTrials("pilot-causals-8-b")

d8b.catch <- d8b.catch %>% mutate(passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))
  
sum(d8b.catch$passBoth)
```

```{r}
d8b <- left_join(readData("pilot-causals-8-b"), d8b.catch %>% select(workerid, passBoth))
```


```{r}

d8b.filtered <- d8b %>% filter(passBoth == 1)

d8b.filtered %>%
  group_by(distribution) %>%
  summarize(n = n()) %>% kable()
```

```{r fig.width = 6}
d8b.summary <- d8b.filtered %>%
  group_by(distribution, frequency) %>%
  multi_boot_standard(column = "response") %>%
  ungroup()

d8b.bayes <- d8b.filtered %>%
  group_by(distribution, frequency) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))
bind_rows(d8.bayes, d8b.bayes) %>% 
  mutate(Distribution = factor(distribution, 
                               levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
         labels = c("Common Deterministic", "Rare Deterministic",
                    "Common Weak", "Rare Weak"))) %>%
ggplot(., aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, fill = Distribution, color = Distribution,
#ggplot(d8.summary, aes( x = factor(frequency), y = mean, ymin = ci_lower, ymax = ci_upper, fill = distribution,
                        group = distribution))+
  geom_bar(stat='identity', position = position_dodge(0.4), width = 0.4, color = 'white')+
  geom_errorbar(width = 0.2, position = position_dodge(0.4), color= 'white')+
  theme(axis.text.x = element_text(angle = 90))+
  geom_hline(yintercept = 0.5, lty = 3, color = 'white')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
  #scale_fill_brewer(palette = 3, type = 'qual')+
  scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
#  scale_fill_manual(values = c("#d7191c", "#fdae61", "#2c7bb6", "#abd9e9"))+
 # scale_color_manual(values = c("#d7191c", "#fdae61", "#2c7bb6", "#abd9e9"))+
  xlab("Frequency")+
  ylab("Proportion Endorsement")+
  theme_black()


# bind_rows(d8.bayes, d8b.bayes) %>% 
#   mutate(Distribution = factor(distribution, 
#                                levels = c("common_deterministic", "rare_deterministic", "common_weak", "rare_weak"),
#          labels = c("Common Deterministic", "Rare Deterministic",
#                     "Common Weak", "Rare Weak"))) %>%
# ggplot(., aes( x = factor(frequency), y = MAP_h, ymin = low, ymax = high, color = Distribution,
# #ggplot(d8.summary, aes( x = factor(frequency), y = mean, ymin = ci_lower, ymax = ci_upper, fill = distribution,
#                         group = distribution))+
#   geom_linerange(position = position_dodge(0.2), size = 2)+
#   #geom_errorbar(width = 0.2, position = position_dodge(0.3), color = 'white')+
#   theme(axis.text.x = element_text(angle = 90))+
#   geom_hline(yintercept = 0.5, lty = 3, color = 'white')+
#   scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5, 1))+
#   #scale_fill_brewer(palette = 3, type = 'qual')+
#   scale_color_manual(values = c("#d7191c", "#fdae61", "#2c7bb6", "#abd9e9"))+
#   xlab("Frequency")+
#   ylab("Proportion Endorsement")+
#   theme_black()


ggsave("~/Documents/research/talks/generics/a-generic-workshop-2017-comgen/img/causals-pilot-8-n400.pdf", width = 5, height = 3)
```



```{r}
ggplot(data.frame(x = rbeta(n = 10000, shape1 = 4, shape2 = 2)), aes(x = x))+ 
  geom_density(fill = "#f1b6da", adjust = 1.3, alpha =0.8, 
               color = "#f1b6da", size = 1.2)+ 
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  theme_black()+
  ylab("Prior Belief")+
  xlab("Target probability")

ggsave("~/Documents/research/talks/generics/a-generic-workshop-2017-comgen/img/a-prior.pdf", width = 5, height = 3)
```


```{r}
sample.dists <- bind_rows(
  data.frame(
    dist = "rare weak",
    x = c(rbeta(n = 3000, shape1 = 2, shape2 = 10),
          rbeta(n = 7000, shape1 = 2, shape2 = 50)
          )
  ),
  data.frame(
    dist = "common weak",
    x = rbeta(n = 10000, shape1 = 2, shape2 = 10)
  ),
  data.frame(
    dist = "rare deterministic",
    x = c(rbeta(n = 3000, shape1 = 50, shape2 = 2),
          rbeta(n = 7000, shape1 = 2, shape2 = 50)
          )
  ),
  data.frame(
    dist = "common deterministic",
    x = rbeta(n = 10000, shape1 = 50, shape2 = 2)
  )
) %>%
    mutate(Distribution = factor(dist, 
                               levels = c("common deterministic", "rare deterministic", "common weak", "rare weak"),
         labels = c("Common Deterministic", "Rare Deterministic",
                    "Common Weak", "Rare Weak")))
  
  
  

ggplot(sample.dists, aes(x = x, fill = Distribution, color = Distribution))+ 
  geom_density( adjust = 1.3, alpha =0.8, 
               size = 1.2,
               aes( y = ..scaled..))+ #
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  theme_black()+
    scale_fill_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
  scale_color_manual(values = c("#d01c8b", "#f1b6da", "#4dac26", "#b8e186"))+
  ylab("Scaled Prior Probability")+
  xlab("Target probability")+
  facet_wrap(~Distribution, scales = 'free')+
  guides(fill = F, color = F)

ggsave("~/Documents/research/talks/generics/a-generic-workshop-2017-comgen/img/causal-manipulated-priors.pdf", width = 5, height = 3)
```



# Causals 8 prior

```{r}
d8.info <- readSubjectInfo("causals-8-prior")

table(d8.info$enjoyment)
```

```{r}
d8.info %>% select(comments) %>%
  filter(comments != "") %>% kable()
```

```{r}
d8.info %>% select(problems) %>%  filter(problems != "") %>%kable()
```



```{r}
d8.prior.catch <- readCatchTrials("causals-8-prior")

mischaracterized <- c( 24, 48, 62, 94, 106, 110, 111, 112, 113, 116, 125, 132, 145, 155, 158)

d8.prior.catch <- d8.prior.catch %>%
  mutate(pass_numeric = ifelse(workerid %in% mischaracterized, 1, pass_numeric),
         passBoth = ifelse(pass_numeric + pass_story == 2, 1, 0))

  
sum(d8.prior.catch$passBoth)
```

Mis-characterized: 24, 48, 62, 94, 106, 110, 111, 112, 113, 116, 125, 132, 145, 155, 158

i think these were mischaracterized because they put "0", or they put "0/100"


```{r}
d8.prior <- readData("causals-8-prior")

d8.prior <- left_join(readData("causals-8-prior"), d8.prior.catch %>% select(workerid, passBoth)) %>%
  filter(passBoth == 1)

```

Time spent on trial

```{r}
d8.prior.rt <- unique(d8.prior %>% select(workerid, rt)) %>%
  mutate(logrt = log(rt / 1000))


d8.prior.rt.stats <- d8.prior.rt %>% 
  summarize(meanRT = mean(rt / 1000),
            sdRT = sd(rt / 1000),
            meanLogRT = mean(logrt),
            sdLogRT = sd(logrt))

ggplot(d8.prior.rt, aes( x = rt/1000))+
  geom_histogram()

```


How many participants per distribution

```{r}
d8.prior %>%
  group_by(distribution, condition) %>%
  summarize(n = n()) %>% 
  mutate(n = ifelse(condition == "prior", n / 5, n)) %>%
  kable()
```


### Prior data

```{r fig.width = 4, fig.height = 5}
ggplot(d8.prior, aes(x = response))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  facet_grid(distribution~., scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))+ ylab("proportion")
  
```

```{r}
ggplot(d8.prior, aes(x = response))+
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  facet_grid(story~., scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))+ ylab("proportion")
```

```{r}
ggplot(d8.prior, aes(x = response))+
  geom_histogram()+
  facet_grid(story~distribution, scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))
```
